Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-06-28 latex/CEUR/paper.tex
Reformatting LaTeX for git i.e. new sentence on each line
Added conclusion

%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
%% \usepackage{minted}
\graphicspath{ {./figures/} }
\usepackage{tcolorbox}
\usepackage{array}
\newcolumntype{N}{>{\centering\arraybackslash}m{.9cm}}
\newcolumntype{M}{>{\centering\arraybackslash}m{1.0cm}}
\newcolumntype{Z}{>{\centering\arraybackslash}m{1.6cm}}
\newcolumntype{L}{>{\centering\arraybackslash}m{2.3cm}}
\usepackage{multirow}
%
%% auto break lines
%% \setminted{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2021}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{CIKM'21: Complex Data Challenges for Earth Observation,
  November 01--05, 2021, Online}

%%
%% The "title" command
\title{Uncertainty-aware graph-based multimodal remote sensing classification}
%

%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Iain~Rolland}[orcid=0000-0002-4137-5605, email=imr27@cam.ac.uk,]

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented document is presented as an article formatted for publication by CEUR-WS in a conference proceedings.
  Based on the ``ceurart'' document class, this article presents and explains many of the common variations, as well as many of the formatting elements an author may use in the preparation of the documentation of their work.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input which describes each node. The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $. For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e. $\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.

@@

where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $\textrm{l}^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function. For the first layer, the weights are $\boldsymbol{W}^{(0)}\in\mathbb{R}^{C\times F}$ and $\mathbf{Z}^{(0)} = \mathbf{X}\in\mathbb{R}^{N\times C}$ where $F$ is the number of features in the layer's output (a hyperparameter of the layer).

@@

In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function. In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node. In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible. This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by

@@

where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$. Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.

@@

It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{pmlr_v48_gal16}. The dropouts are used to represent stochasticity in the model parameters \cite{C9SC01992H}. A given combination of dropouts can be considered to represent a model sampled from the approximate posterior, $q(\boldsymbol{\theta})$, with the actual posterior distribution of models being $p(\boldsymbol{\theta}|\mathcal{D})$. Monte Carlo sampling can be used to approximately compute quantities such as the term $\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]$ in (\ref{eq::epistemic}) allowing the aleatoric and epistemic uncertainty to be calculated. This can be done using the approximation 

@@

where $\boldsymbol{\theta}^m\sim q(\boldsymbol{\theta})$ is a model sampled by performing dropout inference. When this technique has been used, the model name represents this using a `B' in its name, e.g. S-BGCN, showing that this Bayesian approximation has been used. The Drop-GCN model, which is used for benchmarking the subjective methods, refers to the same technique when applied to a `vanilla' GCN.

@@

In order to assist the convergence of subjective models, two additional assistance techniques have been used: teacher knowledge distillation and the use of a Dirichlet prior. These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{Zhao2020}.

@@

By training a non-subjective model in advance, its outputs, $\hat{p}_{ik}$, can be used in order to encourage the subjective model to converge to node Dirichlet distributions with $\mathbb{E}[p_{ik}]$ which are close to the teacher's deterministic estimates. This is achieved using an additional term in the loss function,

@@

which corresponds to the summation of KL-divergence terms between the teacher output probability and the expected value of the subjective model's Dirichlet distribution for each node, $\sum_i\infdiv{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}$. Notice that this sum is computed over all nodes as opposed to just the nodes in $\mathbb{L}$. Models trained using a teacher are denoted using the ``-T'' suffix e.g. a S-BGCN-T model would indicate that a pre-trained GCN was used as a teacher in order to assist the training convergence of a subjective graph convolutional model.

@@

A second convergence assistance technique which can be used involves the use of a Dirichlet prior, $\hat{\boldsymbol{\alpha}}$. The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{huang2021combining}. Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing. If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class is given by

@@

where $\sigma$ is a scale parameter which controls the order of distance magnitude over which evidence will propagate in the prior. The total evidence to suggest the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class, $e_{ik}$ can be found by summing these contributions over the nodes in the training set such that the element in the prior is given by 

@@

A node which is far from all observed nodes, i.e. $h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$. The prior's Dirichlet strength for the $\text{i}^\text{th}$ node, $\hat{S}_i$, will therefore be approximately $K$ and the node's vacuity, as given by (\ref{eq::vacuity}), will be approximately 1. On the other hand, a node which is near to many observed nodes will have large $\hat{S}_i$ and node vacuity will be small. The KL-divergence between the Dirichlet distribution of the prior and the model output can be incorporated into the loss function using the term

@@

which can be incorporated into the total loss. Models trained using a prior are denoted using the ``-K'' suffix e.g. a S-BGCN-K model would indicate that the graph convolutional network was trained with a loss function using a weighted combination of the loss in (\ref{eq:core_loss}) and the term described in (\ref{eq::teacher_loss}).

@@

\subsection{Results and analysis}
\label{sec::results}
\subsection{Data}
A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications.
The modes of data collected come from three sensor types: LiDAR, optical and hyperspectral (HS).
The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT). In order to simplify analysis, the optical data (which was provided at $0.05$ m resolution) and the HS data (which was provided at $1.0$ m resolution) were bilinearly resampled to obtain $0.5$ m resolution across inputs and outputs.

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUROC metric).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$ \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$ \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$ \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$ \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$ \\
GCN & - & - &-&-&$0.887$ \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$ \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
\label{tab::misc_aupr}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
GCN & - & -  &-&-&$0.606$ \\ 
Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUROC metric). Values shown represent the mean $\pm$ standard deviation.}
\label{tab::ood_auroc}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
S-BGCN-T-K (pixel prior) & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ &$0.593\pm0.188$&$0.396\pm0.096$&$0.578\pm0.186$    \\ 
S-BGCN & $0.586\pm0.147$ & $0.666\pm0.132$ &$0.596\pm0.193$&$0.401\pm0.092$&$0.580\pm0.191$    \\ 
S-GCN & $0.580\pm0.145$ & $0.650\pm0.120$ &-&-&$0.586\pm0.181$    \\ 
S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ &-&-&$0.787\pm0.125$    \\   
GCN & - & - &-&-&$0.538\pm0.188$    \\ 
Drop-GCN & - & - &$0.541\pm0.185$&$0.420\pm0.161$&$0.538\pm0.187$    \\ \hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUPR metric). Values shown represent the mean $\pm$ standard deviation.}
\label{tab::ood_aupr}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
S-BGCN-T-K (pixel prior) &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
S-BGCN & $0.127\pm0.186$ & $0.139\pm0.190$  &$0.150\pm0.213$&$0.095\pm0.195$&$0.145\pm0.209$    \\ 
S-GCN & $0.125\pm0.185$ & $0.130\pm0.191$  &-&-&$0.143\pm0.207$    \\ 
S-MLP & $0.245\pm0.214$ & $0.233\pm0.170$ &-&-&$0.219\pm0.201$    \\   
GCN & - & -  &-&-&$0.116\pm0.179$    \\ 
Drop-GCN & - & -  & $0.116\pm0.179$&$0.115\pm0.257$&$0.116\pm0.179$    \\ \hline
\end{tabular}
\end{center}
\end{table*}

@@

\subsection{Title variants}

\subsection{Authors and Affiliations}

\subsection{Abstract and Keywords}

Abstract here.

\section{Sectioning Commands}

\section{Math Equations}

\subsection{Inline (In-text) Equations}

\subsection{Display Equations}

\section{Citations and Bibliographies}

\subsection{Some examples}

\section{Acknowledgments}

%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to the developers of ACM consolidated LaTeX styles
\end{acknowledgments}

%%
%% Define the bibliography file to be used
\bibliography{bibtex/bib/IEEEabrv, bibtex/bib/imrolland}

@@

%%
%% End of file

>>>>

\documentclass[
twocolumn,
% hf,
]{ceurart}

% One can fix some overfulls
\sloppy

% Minted listings support 
% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
% \usepackage{minted}

% Add figures directory as graphics path
\graphicspath{ {./figures/} }

% Used for KL-divergence
\usepackage{mathtools}
\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
  #1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

% Used for colored boxes in class legend table
\usepackage{tcolorbox}
% Custom column widths`
\usepackage{array}
\newcolumntype{N}{>{\centering\arraybackslash}m{.9cm}}
\newcolumntype{M}{>{\centering\arraybackslash}m{1.0cm}}
\newcolumntype{Z}{>{\centering\arraybackslash}m{1.6cm}}
\newcolumntype{Y}{>{\centering\arraybackslash}m{2.3cm}}
\usepackage{multirow}

% auto break lines
% \setminted{breaklines=true}

% end of the preamble, start of the body of the document source.
\begin{document}

% Rights management information.
% CC-BY is default license.
\copyrightyear{2021}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

% This command is for the conference information
\conference{CIKM'21: Complex Data Challenges for Earth Observation,
  November 01--05, 2021, Online}

% The "title" command
\title{Uncertainty-aware graph-based multimodal remote sensing classification}

% The "author" command and its associated commands are used to define
% the authors and their affiliations.
\author[1]{Iain~Rolland}[orcid=0000-0002-4137-5605, email=imr27@cam.ac.uk,]

@@

% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
  A clear and well-documented document is presented as an article formatted for publication by CEUR-WS in a conference proceedings.
  Based on the ``ceurart'' document class, this article presents and explains many of the common variations, as well as many of the formatting elements an author may use in the preparation of the documentation of their work.
\end{abstract}

% Keywords. The author(s) should pick words that accurately describe the work being presented. Separate the keywords with commas.
\begin{keywords}
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

% This command processes the author and affiliation and title information and builds the first part of the formatted document.
\maketitle

@@

The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input which describes each node.
The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $.
For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e. $\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.

@@

where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $\textrm{l}^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function.
For the first layer, the weights are $\boldsymbol{W}^{(0)}\in\mathbb{R}^{C\times F}$ and $\mathbf{Z}^{(0)} = \mathbf{X}\in\mathbb{R}^{N\times C}$ where $F$ is the number of features in the layer's output (a hyperparameter of the layer).

@@

In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function.
In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by

@@

where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$.
Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.

@@

It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{pmlr_v48_gal16}.
The dropouts are used to represent stochasticity in the model parameters \cite{C9SC01992H}.
A given combination of dropouts can be considered to represent a model sampled from the approximate posterior, $q(\boldsymbol{\theta})$, with the actual posterior distribution of models being $p(\boldsymbol{\theta}|\mathcal{D})$.
Monte Carlo sampling can be used to approximately compute quantities such as the term $\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]$ in (\ref{eq::epistemic}) allowing the aleatoric and epistemic uncertainty to be calculated.
This can be done using the approximation 

@@

where $\boldsymbol{\theta}^m\sim q(\boldsymbol{\theta})$ is a model sampled by performing dropout inference.
When this technique has been used, the model name represents this using a `B' in its name, e.g. S-BGCN, showing that this Bayesian approximation has been used.
The Drop-GCN model, which is used for benchmarking the subjective methods, refers to the same technique when applied to a `vanilla' GCN.

@@

In order to assist the convergence of subjective models, two additional assistance techniques have been used: teacher knowledge distillation and the use of a Dirichlet prior.
These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{Zhao2020}.

@@

By training a non-subjective model in advance, its outputs, $\hat{p}_{ik}$, can be used in order to encourage the subjective model to converge to node Dirichlet distributions with $\mathbb{E}[p_{ik}]$ which are close to the teacher's deterministic estimates.
This is achieved using an additional term in the loss function,

@@

which corresponds to the summation of KL-divergence terms between the teacher output probability and the expected value of the subjective model's Dirichlet distribution for each node, $\sum_i\infdiv{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}$.
Notice that this sum is computed over all nodes as opposed to just the nodes in $\mathbb{L}$.
Models trained using a teacher are denoted using the ``-T'' suffix e.g. a S-BGCN-T model would indicate that a pre-trained GCN was used as a teacher in order to assist the training convergence of a subjective graph convolutional model.

@@

A second convergence assistance technique which can be used involves the use of a Dirichlet prior, $\hat{\boldsymbol{\alpha}}$.
The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{huang2021combining}.
Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing.
If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class is given by

@@

where $\sigma$ is a scale parameter which controls the order of distance magnitude over which evidence will propagate in the prior.
The total evidence to suggest the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class, $e_{ik}$ can be found by summing these contributions over the nodes in the training set such that the element in the prior is given by 

@@

A node which is far from all observed nodes, i.e. $h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$.
The prior's Dirichlet strength for the $\text{i}^\text{th}$ node, $\hat{S}_i$, will therefore be approximately $K$ and the node's vacuity, as given by (\ref{eq::vacuity}), will be approximately 1.
On the other hand, a node which is near to many observed nodes will have large $\hat{S}_i$ and node vacuity will be small.
The KL-divergence between the Dirichlet distribution of the prior and the model output can be incorporated into the loss function using the term

@@

which can be incorporated into the total loss.
Models trained using a prior are denoted using the ``-K'' suffix e.g. a S-BGCN-K model would indicate that the graph convolutional network was trained with a loss function using a weighted combination of the loss in (\ref{eq:core_loss}) and the term described in (\ref{eq::teacher_loss}).

@@

\section{Results and analysis}
\label{sec::results}
\subsection{Data}
A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications.
The modes of data collected come from three sensor types: LiDAR, optical and hyperspectral (HS).
The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT).
In order to simplify analysis, the optical data (which was provided at $0.05$ m resolution) and the HS data (which was provided at $1.0$ m resolution) were bilinearly resampled to obtain $0.5$ m resolution across inputs and outputs.

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUROC metric).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Yccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$ \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$ \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$ \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$ \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$ \\
GCN & - & - &-&-&$0.887$ \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$ \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
\label{tab::misc_aupr}
\small
\begin{center}
\begin{tabular}{Yccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
GCN & - & -  &-&-&$0.606$ \\ 
Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUROC metric). Values shown represent the mean $\pm$ standard deviation.}
\label{tab::ood_auroc}
\small
\begin{center}
\begin{tabular}{Yccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
S-BGCN-T-K (pixel prior) & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ &$0.593\pm0.188$&$0.396\pm0.096$&$0.578\pm0.186$    \\ 
S-BGCN & $0.586\pm0.147$ & $0.666\pm0.132$ &$0.596\pm0.193$&$0.401\pm0.092$&$0.580\pm0.191$    \\ 
S-GCN & $0.580\pm0.145$ & $0.650\pm0.120$ &-&-&$0.586\pm0.181$    \\ 
S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ &-&-&$0.787\pm0.125$    \\   
GCN & - & - &-&-&$0.538\pm0.188$    \\ 
Drop-GCN & - & - &$0.541\pm0.185$&$0.420\pm0.161$&$0.538\pm0.187$    \\ \hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUPR metric). Values shown represent the mean $\pm$ standard deviation.}
\label{tab::ood_aupr}
\small
\begin{center}
\begin{tabular}{Yccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
S-BGCN-T-K (pixel prior) &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
S-BGCN & $0.127\pm0.186$ & $0.139\pm0.190$  &$0.150\pm0.213$&$0.095\pm0.195$&$0.145\pm0.209$    \\ 
S-GCN & $0.125\pm0.185$ & $0.130\pm0.191$  &-&-&$0.143\pm0.207$    \\ 
S-MLP & $0.245\pm0.214$ & $0.233\pm0.170$ &-&-&$0.219\pm0.201$    \\   
GCN & - & -  &-&-&$0.116\pm0.179$    \\ 
Drop-GCN & - & -  & $0.116\pm0.179$&$0.115\pm0.257$&$0.116\pm0.179$    \\ \hline
\end{tabular}
\end{center}
\end{table*}

@@

\section{Conclusion}
\label{sec::conclusion}

The misclassification and OOD detection performance of the S-BGCN-T-K presented represents a promising avenue for uncertainty-aware learning.
The uncertainties which are produced by this model can be used to better distinguish misclassified nodes and OOD nodes than any of the other methods which are presented.
Models which are capable of better quantifying confidence in this way are important for real-world applications where the consequences of misplaced model certainty can be high-stake.

The improved estimate of uncertainty obtained through the use of a prior is shown in the S-BGCN-T-K results, with equivalent models which do not use a prior, e.g. S-BGCN-T, producing uncertainty measures which cannot identify misclassified or OOD nodes as successfully.
In order to distinguish misclassifications, the S-BGCN-T-K model measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance.
For the task of identifying nodes which come from a distribution other than the distributions on which the model was trained, the measure of vacuity stands out as the uncertainty metric which does this most successfully.

%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to ...
\end{acknowledgments}

% Define the bibliography file to be used
\bibliography{bibtex/bib/IEEEabrv, bibtex/bib/imrolland}

@@
